### 2022-06-27 latex/MScAIFrancoisBerrier.tex
update

\usepackage[utf8]{inputenc} % Required for inputting international characters
\usepackage[T1]{fontenc} % Output font encoding for international characters
\usepackage{mathpazo} % Use the Palatino font by default
\usepackage[T5,T1]{fontenc}
\usepackage[backend=bibtex,style=authoryear,natbib=true]{biblatex} % Use the bibtex backend with the authoryear citation style (which resembles APA)
\usepackage{float}
\usepackage{lscape}
\usepackage{pdflscape}
\usepackage{rotating}
\usepackage[paper=portrait,pagesize]{typearea}
\usepackage{logicpuzzle}
\newenvironment{fifteen}[1][]{%
\begin{logicpuzzle}[rows=4,columns=4,#1]
\begin{puzzleforeground}
\framepuzzle
\end{puzzleforeground}
}{\end{logicpuzzle}}

@@

\begin{abstract}
\addchaptertocentry{\abstractname} % Add the abstract to the table of contents
\textbf{Motivation}
\\
Reinforcement Learning (\textbf{RL}), exposed with brilliant clarity in the Sutton book (\cite{Sutton1998}), has until recently known less success than we might have hoped for. Its framework is very appealing and intuitive. In particular, the mathematical beauty of Value iteration and Q iteration (\cite{WatkinsThesis}) for discrete state and action spaces, blindly iterating from \textit{any} initial value, is quite prfound. Sadly, it had until recently proven hard to achieve practical success with these methods.
\\
Inspired however by the seminal success of Deep Mind's team in using Deep Reinforcement Learning (\textbf{DRL}) to play Atari games (\cite{Mnih2013})  and to master the game of Go (\cite{AlphaGo}), researchers have in recent years made a lot of progress towards designing algorihtms capable of learning and solving, \textit{without human knowledge}, the Rubiks Cube (\textbf{RC}) - as well as similar single player puzzles - by using Deep Q-Learning (\textbf{DQR})  (\cite{DBLP:journals/corr/abs-1805-07470}) or search and (\textbf{DRL}) value iteration (\cite{https://doi.org/10.48550/arxiv.1805.07470}).
\\
In this project, I will attempt to implement a variety of solvers combining $A^{*}$ search and heuristics, some of which will be handcrafted, others which I will train on randomly generated sequences of puzzles using (\textbf{DL}) or (\textbf{DRL}), to solve the 15-puzzle (and variations of different dimensions), as well as the Rubik's cube.
\\
\\
\textbf{Organisation of this thesis}
\\
In the first chapter, I will quickly describe what I hope to get out of this project, both in terms of personal learning, as well as in terms of tangible results (solving some puzzles!). In chapter 2, I will do a quick recap of the different methods that I will use in the project. Chapter 3 will be dedicated to discussing the mathematics of the sliding puzzle (\textbf{SP}) and the (\textbf{RC}). I might throw a few random (but hopefully interesting) observations in there and give some references for the keen reader. I will then give an overview in chapter 4 of the code base I have developed - and put in the open on my github page (\cite{FB}) - to complete this project. Finally, in chapters 5 and 6, I will present all my various results on respecively the sliding puzzle and the Rubiks' cube.

@@

\begin{acknowledgements}
\addchaptertocentry{\acknowledgementname} % Add the acknowledgements to the table of contents
I am grateful to my employer Bank of America for sponsoring my part time 2-year MSc in Artificial Intelligence at Royal Holloway. I entered in the study of AI with a heavy dose of skepticism and am delighted to have learnt so much and revised my judgment of this field.
In particular I would like to thank my managers Mitrajit Dutta and Stephen Thompson for supporting me in pursuing this MSc.
\\
\\
I have been fortunate to have had the company of my colleague Saurabh Kumar, as he decided to follow me in this MSc journey. We have had countless opportunities to debate about all the new cool stuff we learnt during the MSc, and that has definitely made the whole process much more enjoyable.
\\
\\
I would also like to thank Professor Chris Watkins, inventor of QL :), for agreeing to supervise my project. It was an honour to attend his very lively lectures on Deep Learning during the first year of the MSc, as well as to absorb some of his wisdom and enthusiasm at our meetings during my work on this project.
\\
\\
Last but not least, my wife Thanh Nh\~a is my biggest supporter in everything I do, and her continued encouragement and enthusiasm in my pursuit of this MSc has made it so much easier to juggle between a demanding banking job, running 50 to 60 miles a week in preparation of multiple marathons and half marathons, and the coursework, lectures and exam revisions.
\end{acknowledgements}

%----------------------------------------------------------------------------------------
%	LIST OF CONTENTS/FIGURES/TABLES PAGES
%----------------------------------------------------------------------------------------

>>>>

\usepackage[utf8]{inputenc} % Required for inputting international characters
\usepackage[T1]{fontenc} % Output font encoding for international characters
\usepackage{mathpazo} % Use the Palatino font by default
\usepackage[T5,T1]{fontenc}
\usepackage{verbatim}
\usepackage[backend=bibtex,style=authoryear,natbib=true]{biblatex} % Use the bibtex backend with the authoryear citation style (which resembles APA)
\usepackage{float}
\usepackage{lscape}
\usepackage{pdflscape}
\usepackage{rotating}
\usepackage[paper=portrait,pagesize]{typearea}
\usepackage{logicpuzzle}
\newenvironment{fifteen}[1][]{%
\begin{logicpuzzle}[rows=4,columns=4,#1]
\begin{puzzleforeground}
\framepuzzle
\end{puzzleforeground}
}{\end{logicpuzzle}}

@@

\begin{abstract}
\addchaptertocentry{\abstractname} % Add the abstract to the table of contents
\textbf{Motivation}
\\
Reinforcement Learning (\textbf{RL}), exposed with brilliant clarity in the Sutton book (\cite{Sutton1998}), has until recently known less success than we might have hoped for. Its framework is very appealing and intuitive. In particular, the mathematical beauty of Value iteration and Q iteration (\cite{WatkinsThesis}) for discrete state and action spaces, blindly iterating from \textit{any} initial value, is quite profound. Sadly, it had until recently proven hard to achieve practical success with these methods.
\\
Inspired however by the seminal success of Deep Mind's team in using Deep Reinforcement Learning (\textbf{DRL}) to play Atari games (\cite{Mnih2013})  and to master the game of Go (\cite{AlphaGo}), researchers have in recent years made a lot of progress towards designing algorithms capable of learning and solving, \textit{without human knowledge}, the Rubiks Cube (\textbf{RC}) - as well as similar single player puzzles - by using Deep Q-Learning (\textbf{DQR})  (\cite{DBLP:journals/corr/abs-1805-07470}) or search and (\textbf{DRL}) value iteration (\cite{https://doi.org/10.48550/arxiv.1805.07470}).
\\
In this project, I will attempt to implement a variety of solvers combining $A^{*}$ search and heuristics, some of which will be handcrafted, others which I will train on randomly generated sequences of puzzles using (\textbf{DL}) or (\textbf{DRL}), to solve the 15-puzzle (and variations of different dimensions), as well as the Rubik's cube.
\\
\\
\textbf{Organisation of this thesis}
\\
In the first chapter, I will quickly describe what I hope to get out of this project, both in terms of personal learning, as well as in terms of tangible results (solving some puzzles!). In chapter 2, I will do a quick recap of the different methods that I will use in the project. Chapter 3 will be dedicated to discussing the mathematics of the sliding puzzle (\textbf{SP}) and the (\textbf{RC}). I might throw a few random (but hopefully interesting) observations in there and give some references for the keen reader. I will then give an overview in chapter 4 of the code base I have developed - and put in the open on my github page (\cite{FB}) - to complete this project. Finally, in chapters 5 and 6, I will present all my various results on respecively the sliding puzzle and the Rubiks' cube.

@@

\begin{acknowledgements}
\addchaptertocentry{\acknowledgementname} % Add the acknowledgements to the table of contents
\begin{comment}
I am grateful to my employer Bank of America for sponsoring my part time 2-year MSc in Artificial Intelligence at Royal Holloway. I entered in the study of AI with a heavy dose of skepticism and am delighted to have learnt so much and revised my judgment of this field.
In particular I would like to thank my managers Mitrajit Dutta and Stephen Thompson for supporting me in pursuing this MSc.
\\
\\
I have been fortunate to have had the company of my colleague Saurabh Kumar, as he decided to follow me in this MSc journey. We have had countless opportunities to debate about all the new cool stuff we learnt during the MSc, and that has definitely made the whole process much more enjoyable.
\\
\\
I would also like to thank Professor Chris Watkins, inventor of QL :), for agreeing to supervise my project. It was an honour to attend his very lively lectures on Deep Learning during the first year of the MSc, as well as to absorb some of his wisdom and enthusiasm at our meetings during my work on this project.
\\
\\
Last but not least, my wife Thanh Nh\~a is my biggest supporter in everything I do, and her continued encouragement and enthusiasm in my pursuit of this MSc has made it so much easier to juggle between a demanding banking job, running 50 to 60 miles a week in preparation of multiple marathons and half marathons, and the coursework, lectures and exam revisions.
\end{comment}
\end{acknowledgements}
%----------------------------------------------------------------------------------------
%	LIST OF CONTENTS/FIGURES/TABLES PAGES
%----------------------------------------------------------------------------------------
